geochemistry

### 2025-02-13 geochemistry.qmd
XRD plot (tested and running) because post-operations means working until 2 am while we wait for the next batch of pain killers.

library(readr)
library(dplyr)
library(janitor)
library(tidyr)
library(gt)
library(ggplot2)
library(cowplot)
library(tidyverse)
library(ggfortify)
library(FactoMineR)
library(factoextra)

@@

>>>>

library(readr)
library(dplyr)
library(janitor)
library(tidyr)
library(gt)
library(ggplot2)
library(cowplot)
library(tidyverse)
library(ggfortify)
library(FactoMineR)
library(factoextra)
library(powdR)

@@

```{r}
#| label: xrd-graphs

sp6_xrd <- read_csv('data/SP6_xrd.csv')
sp6_peaks <- read_csv('data/SP6_CSV_PEAKS.csv')

sp6_long <- sp6_xrd %>%
  pivot_longer(cols = c(Difference, Background, Observed, SiO2, Dolomite), 
               names_to = "Phase", 
               values_to = "Count")

p_sp6 <- sp6_long |> 
  mutate(Phase = factor(Phase, levels = c("Difference", "Observed", "SiO2", "Dolomite", "Background"))) |>
  ggplot(aes(x = Baseline, y = Count, color = Phase)) +
  geom_line(size = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  geom_point(data = sp6_peaks, aes(x = Angle, y = Intensity, colour = Phase), size = 5,
             shape = 21, show.legend = FALSE) +
  geom_label(data = sp6_peaks, aes(x = Angle, y = Intensity, label = d), 
             size = 3, fill = "white", label.size = 0.2, vjust = -0.8, show.legend = FALSE)
```
